### 2017-06-18 paper/lexicographic.tex
started section on application of LexRSMs to prob programs

Since the constraint~\eqref{eq:cond-exp} defining conditional expectation is phrased in terms of expected values, the almost-sure uniqueness cannot be strengthened to uniqueness, as re-defining a random variable on a set of probability zero does not change its expectation. In the following, when we say that a conditional expectation of a random variable $X$ satisfies some inequality (e.g. $\E[X\mid\mathcal{F}]\geq 0$) on set $L\subseteq \Omega$, we mean that for each $\mathcal{F}$-measurable function $\E[X\mid\mathcal{F}]$ satisfying~\eqref{eq:cond-exp} the inequality is satisfied for almost all $\omega \in L$.

>>>>

Since the constraint~\eqref{eq:cond-exp} defining conditional expectation is phrased in terms of expected values, the almost-sure uniqueness cannot be strengthened to uniqueness, as re-defining a random variable on a set of probability zero does not change its expectation. In the following, when we say that a conditional expectation of a random variable $X$ satisfies some inequality (e.g. $\E[X\mid\mathcal{F}]\geq 0$) on set $L\subseteq \Omega$, we mean that for each $\mathcal{F}$-measurable function $\E[X\mid\mathcal{F}]$ satisfying~\eqref{eq:cond-exp} the .

### 2017-06-18 paper/prelims.tex
corrected some stuff about conditional expectation
started section on application of LexRSMs to prob programs

\smallskip\noindent{\em Variables and valuations.}
Throughout the paper we fix a countable set of variables $\vars$. 
We consider some arbitrary but fixed linear order on the set of all variables. 
Hence, given some set of variables $V$ we can enumerate its members in 
ascending order (w.r.t. the fixed ordering) and write 
$V=\{x_1,x_2,x_3,\dots\}$. 
%A \emph{valuation} is a partial function 
%$\val\colon 
%\vars \dashrightarrow \Rset$ assigning a unique number to some of the 
%variables. A \emph{domain} of a valuation $\val$, denoted by %$\dom(\val)$, is 
%the set of all variables $x$ such that $\val(x)$ is defined. Given a %set 
%$\pvars\subseteq \vars$ of variables, we denote by $\vals(\pvars)$ the %set of 
%all valuations $\val$ with $\dom(\val)=\pvars$.

@@

\smallskip\noindent{\em Affine Expressions.}
An \emph{affine expression} over the set of variables $\{x_1,\dots,x_n\}$ is an 
expression of the form $d+\sum_{i=1}^{n}a_i
x_i$, where  $d,a_1,\dots,a_n$ are real-valued
constants.  A function of the form $E(\vec{x})$ for some affine expression $E$ 
is called affine. As noted above
%Following the terminology of~\cite{DBLP:conf/sas/KatoenMMM10} we fix the
%following nomenclature

\smallskip\noindent{\em Predicates}
A \emph{predicate} is a logical formula obtained by a finite number of applications of conjunction, disjunction and negation operations on \emph{atomic predicates} of the form $E(\vec{x})\leq E'(\vec{y})$, where $E$, $E'$ are expressions.

@@

>>>>

\smallskip\noindent{\em Variables.}
Throughout the paper we fix a countable set of variables $\vars$. 
We consider some arbitrary but fixed linear order on the set of all variables. 
Hence, given some set of variables $V$ we can enumerate its members in 
ascending order (w.r.t. the fixed ordering) and write 
$V=\{x_1,x_2,x_3,\dots\}$. 
%A \emph{valuation} is a partial function 
%$\val\colon 
%\vars \dashrightarrow \Rset$ assigning a unique number to some of the 
%variables. A \emph{domain} of a valuation $\val$, denoted by %$\dom(\val)$, is 
%the set of all variables $x$ such that $\val(x)$ is defined. Given a %set 
%$\pvars\subseteq \vars$ of variables, we denote by $\vals(\pvars)$ the %set of 
%all valuations $\val$ with $\dom(\val)=\pvars$.

@@

\smallskip\noindent{\em Affine Expressions.}
An \emph{affine expression} over the set of variables $\{x_1,\dots,x_n\}$ is an 
expression of the form $d+\sum_{i=1}^{n}a_i
x_i$, where  $d,a_1,\dots,a_n$ are real-valued
constants.  A function of the form $E(\vec{x})$ for some affine expression $E$ 
is called affine. As noted above, each affine function is Borel-measurable.
%Following the terminology of~\cite{DBLP:conf/sas/KatoenMMM10} we fix the
%following nomenclature

\smallskip\noindent{\em Predicates.}
A \emph{predicate} is a logical formula obtained by a finite number of applications of conjunction, disjunction and negation operations on \emph{atomic predicates} of the form $E\leq E'$, where $E$, $E'$ are expressions.

@@

Following the usual probabilistic terminology, we say that \emph{almost all} $\omega$ belonging to some set $O\subseteq \Omega$ satisfy some property $\Psi$ if it holds that $\probm{(\{\omega\in O\mid \omega \text{ does not satisfy }\Psi\})}=0$.
